iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-29 manuscript/main.tex
Cleaned up conclusion and rearranged sundries.

\section*{Conclusion}
iSEE provides a general interactive interface for visual exploration of a diverse range of `-omics data sets.
We provide a number of demonstrations at \url{https://github.com/LTLA/iSEE2018}, using iSEE to explore the TCGA RNA-seq collection \citep{piccolo2015TCGA}, the 4,000 PBMC single-cell RNA sequencing data set from 10X Genomics \citep{zheng2017massively} and a published mass cytometry data set consisting of over 170,000 cells \citep{bodenmiller2012cytof}.
% TODO: repurpose the conclusion if we showcase the examples in earlier sections
% TODO: sell the idea that for every data set it is possible to explore and showcase feats of interest. Something like...
We expect the functionalities and flexibility of the iSEE package to be essential for exploring and showcasing relevant features of any data set that can be represented in the form of a SummarizedExperiment object.
In particular, we expect public instances of iSEE to ideally accompany publications, as they enable authors to reproduce published figures and showcase salient aspects of their work using guided tours, while fostering hypothesis generation through transparent, interactive, reproducible, and efficient data analysis by the broader reader audience.

\subsection*{Author contributions}
All authors contributed conceptually and technically to the development and maintenance of large sections of the package code.
A.T.L.L. and F.M. developed the application and data infrastructure.
K.R.A and C.S. developed the plotting framework.
F.M. developed the code tracking and user interface.
K.R.A designed and developed the ExperimentColorMap class.
All authors contributed to testing the application on all data sets.
All authors wrote and approved the final manuscript.

\subsection*{Data and software availability}
The iSEE package is available at \url{https://bioconductor.org/packages/iSEE}

Source code of the development version is available at \url{https://github.com/csoneson/iSEE}

Archived source code as at the time of publication is available at % TODO

An instance of the package running on a public Shiny Server is available at \url{http://shiny.imbei.uni-mainz.de:3838/iSEE/}

% TODO: docker/singularity containers

% TODO:conda pkg
% The iSEE package is also distributed via the bioconda channel for the conda package manager at...https://anaconda.org/bioconda/bioconductor-isee % still needs to be finalized!!

Software license: MIT

\subsection*{Competing interests}
All financial, personal, or professional competing interests for any of the authors that
could be construed to unduly influence the content of the article must be disclosed and
will be displayed alongside the article.

\subsection*{Grant information}
ATLL was supported by core funding from Cancer Research UK (award no. 17197 to Dr.\ John Marioni).
The work of FM is supported by the German Federal Ministry of Education and Research (BMBF 01EO1003).

\subsection*{Acknowledgements}
We thank the organizers and participants of the European Bioconductor Meeting 2017, where the idea for this package was first conceived.
We also thank members of the Bioconductor community for their helpful suggestions.

>>>>

\section*{Conclusion}
iSEE provides a general interactive interface for visual exploration of high-throughput biological data sets.
Any study that can be represented in a SummarizedExperiment object can be used as input, allowing iSEE to accommodate a diverse range of `-omics data sets.
The interface is flexible and can be dynamically customized by the user; supports exploration of interactions between data aspects through colouring and linking between panels;
and provides transparency and reproducibility during the interactive analysis, through code tracking and state reporting. 
The most obvious use of iSEE is that of data exploration for hypothesis generation during the course of a research project.
However, we also anticipate that public instances of iSEE will accompany publications to enable authors to showcase salient aspects of their work using guided tours.

\section*{Data and software availability}
The iSEE package is available at \url{https://bioconductor.org/packages/iSEE}.
Source code of the development version of the package is available at \url{https://github.com/csoneson/iSEE}.
Code for the demonstrations and tours is available at \url{https://github.com/LTLA/iSEE2018}.

\section*{Author contributions}
All authors contributed conceptually and technically to the development and maintenance of large sections of the package code.
A.T.L.L. and F.M. developed the application and data infrastructure.
K.R.A and C.S. developed the plotting framework.
F.M. developed the code tracking and user interface.
K.R.A designed and developed the ExperimentColorMap class.
All authors contributed to testing the application on all data sets.
All authors wrote and approved the final manuscript.

\section{Competing interests}
No competing interests were declared.

\section{Grant information}
ATLL was supported by core funding from Cancer Research UK (award no. 17197 to Dr.\ John Marioni).
The work of FM is supported by the German Federal Ministry of Education and Research (BMBF 01EO1003).

\section{Acknowledgements}
We thank the organizers and participants of the European Bioconductor Meeting 2017, where the idea for this package was first conceived.
We also thank members of the Bioconductor community for their helpful suggestions.
